When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-04-03 presentation/inbreeding.Rmd
Final changes before talk

**Increased mate relatedness and inbreeding depression will cause optimal parental investment to increase**

>>>>

**Higher mate relatedness & inbreeding depression causes optimal parental investment to increase**

<span style="font-size: 14px;">
Duthie, AB & JM Reid (2015) *PLoS One* [10:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf) [SI](https://bradduthie.github.io/Duthie%26Reid2015SI.pdf) [[code]](https://github.com/bradduthie/Duthie_and_Reid_2015_Figs); Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf) [A1](https://bradduthie.github.io/Duthie_Reid2016_AppendixA.pdf) [A2](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf) [SI](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf) [[code]](https://github.com/bradduthie/Inbreeding); Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf) [SI-1](https://bradduthie.github.io/DuthieEtAl2016_SI1.pdf) [SI-2](https://bradduthie.github.io/DuthieEtAl2016_SI2.pdf) [[code]](https://github.com/bradduthie/PolyInbreed); Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf) [SI](https://bradduthie.github.io/DuthieEtAl2017_SI.pdf) [[code]](https://github.com/bradduthie/pre_post_cop);  Duthie, AB et al. (2016) *Proc. R. Soc. B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf) [SI](https://bradduthie.github.io/DuthieEtAl2016c_SI.pdf) [[code]](https://github.com/bradduthie/Inbreeding_Care); Reid, JM et al. (2015) *Evolution* [**70**:1512-1529](https://bradduthie.github.io/ReidEtAl2015c.pdf); Reid, JM et al. (2016) *Evolution* [**69**:2846-2861](https://bradduthie.github.io/ReidEtAl2015c.pdf); <br> Reid, JM et al. (2015) *J. Anim. Ecol.* [84:1029-1040](https://bradduthie.github.io/ReidEtAl2015b.pdf); Reid, JM et al. (2015) *Evolution* [69:59-74](https://bradduthie.github.io/ReidEtAl2015.pdf)
</span>
